Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Fixed \closednote command
Added Rafael as a co-author. Updates in acknowledgement.

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[2]{\pdfmargincomment[color=red,author=#1,open=true]{#2}}
\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\closednote}[4]{\pdfmargincomment[color=gray,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}
\newcommand{\answerednote}[4]{\pdfmargincomment[color=green,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}

@@

\author[mcgill]{Reza Adalat}
\author[mcgill]{Natacha Beck}
\author[mcgill]{Najmeh Khalili-Mahani}
\author[criugm]{Pierre-Olivier Quirion}
\author[mcgill]{Pierre Rioux}

@@

\address[mcgill]{McGill Centre for Integrative Neuroscience, Montreal Neurological Institute, McGill University, Canada.}
\address[creatis]{University of Lyon, CNRS, INSERM, CREATIS, Villeurbanne, France.}
\address[criugm]{Centre de Recherche de l'Institut de G\'eriatrie de Montr\'eal CRIUGM, Montreal, QC, Canada.}

@@

We warmly thank Rafael Ferreira da Silva for its contribution to the
VIP platform and for creating Figure~\ref{fig:vip-architecture}. This
work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work has been made possible with the support of the Irving
Ludmer Family Foundation and the Ludmer Centre for Neuroinformatics
and Mental Health. \note{Marc-e}{Would it be proper to thank EGI? Compute Canada? CANARIE?}

>>>>

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[2]{\pdfmargincomment[color=red,author=#1,open=true]{#2}}
\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\closednote}[4]{\pdfmargincomment[color=gray,author=#1-#3,open=false]{#1: #2 \textCR \textCR #3: #4}}
\newcommand{\answerednote}[4]{\pdfmargincomment[color=green,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}

@@

\author[mcgill]{Reza Adalat}
\author[mcgill]{Natacha Beck}
\author[isi]{Rafael Ferreira da Silva}
\author[mcgill]{Najmeh Khalili-Mahani}
\author[criugm]{Pierre-Olivier Quirion}
\author[mcgill]{Pierre Rioux}

@@

\address[mcgill]{McGill Centre for Integrative Neuroscience, Montreal Neurological Institute, McGill University, Canada.}
\address[creatis]{University of Lyon, CNRS, INSERM, CREATIS, Villeurbanne, France.}
\address[criugm]{Centre de Recherche de l'Institut de G\'eriatrie de Montr\'eal CRIUGM, Montreal, QC, Canada.}
\address[isi]{University of Southern California, Information Sciences Institute, Marina del Rey, CA, USA.}

@@

This work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work also falls into the scope of the scientific topics of
the French National Grid Institute (IdG). We thank the site
administrators of the European Grid Initiative and the GGUS support
for their help related to the VIP platform. We are grateful for the
computing cycles, storage, and support obtained from Compute Canada
(\url{https://computecanada.ca}) for CBRAIN. This work has been made
possible with the support of the Irving Ludmer Family Foundation and
the Ludmer Centre for Neuroinformatics and Mental
Health. \answerednote{Marc-e}{Would it be proper to thank EGI?
  Compute Canada? CANARIE?}{Tristan}{Added EGI and Compute Canada. Not sure if
  Canarie should be added. What about Calcul QC?}
